In mammals, an important proportion of advantageous mutations are repairing damaged genomes instead of creating adaptive innovations

### 2022-10-11 manuscript/supp-mat.tex
Updated manuscript

            \bottomrule
            \endlastfoot
            Equus c. & Equus caballus & $ 0.002$ & $ 0.115$ & $ 1.187$ \\
            Iran & Bos taurus & $ 0.005$ & $ 0.125$ & $ 1.322$ \\
            Uganda & Bos taurus & $ 0.006$ & $ 0.126$ & $ 1.363$ \\
            Australia & Capra hircus & $ 0.003$ & $ 0.122$ & $ 1.035$ \\
            France & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.043$ \\
            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.123$ & $ 1.042$ \\
            Iran & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.052$ \\
            Italy & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.037$ \\
            Morocco & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.057$ \\
            Iran & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.180$ \\
            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.187$ \\
            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.172$ \\
            Various & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.182$ \\
            Morocco & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.189$ \\
            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.123$ & $ 1.341$ \\
            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.370$ \\
            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.361$ \\
            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.359$ \\
            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.125$ & $ 1.371$ \\
            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.124$ & $ 1.349$ \\
            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.126$ & $ 1.391$ \\
            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.125$ & $ 1.362$ \\
            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.362$ \\
            African & Homo sapiens & $ 0.003$ & $ 0.104$ & $ 1.475$ \\
            Admixed American & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.466$ \\
            East Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.478$ \\
            European & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.461$ \\
            South Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.473$ \\
        \end{longtable*}
    \end{center}
    \begin{itemize}
        \item Tajima $\theta$ is the synonymous diversity.
        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
    \end{itemize}

@@

            Equus c. & Equus caballus & $ 0.002$ & $ 0.018$ & $ 0.042$ & $ 0.443$ & $ 0.404$ & $ 0.179$ \\
            Iran & Bos taurus & $ 0.005$ & $ 0.017$ & $ 0.036$ & $ 0.471$ & $ 0.368$ & $ 0.173$ \\
            Uganda & Bos taurus & $ 0.006$ & $ 0.017$ & $ 0.035$ & $ 0.490$ & $ 0.369$ & $ 0.181$ \\
            Australia & Capra hircus & $ 0.003$ & $ 0.017$ & $ 0.036$ & $ 0.488$ & $ 0.144$ & $ 0.070$ \\
            France & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.034$ & $ 0.515$ & $ 0.168$ & $ 0.086$ \\
            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.035$ & $ 0.493$ & $ 0.093$ & $ 0.046$ \\
            Iran & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.030$ & $ 0.589$ & $ 0.140$ & $ 0.083$ \\
            Italy & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.032$ & $ 0.545$ & $ 0.150$ & $ 0.081$ \\
            Morocco & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.029$ & $ 0.598$ & $ 0.137$ & $ 0.082$ \\
            Iran & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.022$ & $ 0.802$ & $ 0.046$ & $ 0.037$ \\
            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.025$ & $ 0.718$ & $ 0.071$ & $ 0.051$ \\
            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.028$ & $ 0.642$ & $ 0.220$ & $ 0.141$ \\
            Various & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.024$ & $ 0.748$ & $ 0.108$ & $ 0.081$ \\
            Morocco & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.020$ & $ 0.883$ & $ 0.070$ & $ 0.062$ \\
            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.040$ & $ 0.375$ & $ 0.374$ & $ 0.140$ \\
            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.040$ & $ 0.377$ & $ 0.368$ & $ 0.139$ \\
            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.031$ & $ 0.482$ & $ 0.377$ & $ 0.182$ \\
            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.035$ & $ 0.428$ & $ 0.308$ & $ 0.132$ \\
            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.037$ & $ 0.404$ & $ 0.368$ & $ 0.149$ \\
            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.039$ & $ 0.388$ & $ 0.368$ & $ 0.143$ \\
            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.038$ & $ 0.392$ & $ 0.368$ & $ 0.144$ \\
            African & Homo sapiens & $ 0.003$ & $ 0.015$ & $ 0.038$ & $ 0.403$ & $ 0.604$ & $ 0.243$ \\
            Admixed American & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.409$ & $ 0.574$ & $ 0.235$ \\
            East Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.426$ & $ 0.484$ & $ 0.206$ \\
            European & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.414$ & $ 0.517$ & $ 0.214$ \\
            South Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.428$ & $ 0.532$ & $ 0.227$ \\

@@

%    \begin{center}
%        \captionof{table}{~}
%        \scriptsize
%        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
%            \toprule
%            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [\Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[\Spop > 0]}$ & $\mathbb{P} [\Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0|\Spop > 0]$ \\
%            \midrule
%            \endhead
%            \midrule
%            \multicolumn{8}{r}{{Continued on next page}} \\
%            \midrule
%            \endfoot
%%
%            \bottomrule
%            \endlastfoot
%            Equus c. & Equus caballus & $ 0.002$ & $ 0.054$ & $ 0.113$ & $ 0.473$ & $ 0.489$ & $ 0.231$ \\
%            Iran & Bos taurus & $ 0.005$ & $ 0.053$ & $ 0.098$ & $ 0.540$ & $ 0.368$ & $ 0.198$ \\
%            Uganda & Bos taurus & $ 0.006$ & $ 0.053$ & $ 0.094$ & $ 0.558$ & $ 0.419$ & $ 0.234$ \\
%            Australia & Capra hircus & $ 0.003$ & $ 0.054$ & $ 0.096$ & $ 0.557$ & $ 0.126$ & $ 0.070$ \\
%            France & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.092$ & $ 0.583$ & $ 0.297$ & $ 0.173$ \\
%            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.096$ & $ 0.561$ & $ 0.080$ & $ 0.045$ \\
%            Iran & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.080$ & $ 0.667$ & $ 0.281$ & $ 0.188$ \\
%            Italy & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.087$ & $ 0.617$ & $ 0.304$ & $ 0.187$ \\
%            Morocco & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.079$ & $ 0.679$ & $ 0.131$ & $ 0.089$ \\
%            Iran & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.060$ & $ 0.897$ & $ 0.304$ & $ 0.273$ \\
%            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.067$ & $ 0.806$ & $ 0.345$ & $ 0.278$ \\
%            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.075$ & $ 0.720$ & $ 0.464$ & $ 0.334$ \\
%            Various & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.064$ & $ 0.840$ & $ 0.359$ & $ 0.302$ \\
%            Morocco & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.055$ & $ 0.971$ & $ 0.247$ & $ 0.240$ \\
%            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.109$ & $ 0.463$ & $ 0.350$ & $ 0.162$ \\
%            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.094$ & $ 0.537$ & $ 0.225$ & $ 0.121$ \\
%            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.108$ & $ 0.466$ & $ 0.312$ & $ 0.145$ \\
%            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.084$ & $ 0.602$ & $ 0.286$ & $ 0.172$ \\
%            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.095$ & $ 0.529$ & $ 0.196$ & $ 0.104$ \\
%            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.101$ & $ 0.500$ & $ 0.296$ & $ 0.148$ \\
%            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.050$ & $ 0.094$ & $ 0.534$ & $ 0.243$ & $ 0.130$ \\
%            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.106$ & $ 0.473$ & $ 0.309$ & $ 0.146$ \\
%            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.104$ & $ 0.485$ & $ 0.245$ & $ 0.119$ \\
%            African & Homo sapiens & $ 0.003$ & $ 0.051$ & $ 0.103$ & $ 0.497$ & $ 0.785$ & $ 0.390$ \\
%            Admixed American & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.104$ & $ 0.492$ & $ 0.737$ & $ 0.363$ \\
%            East Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.098$ & $ 0.521$ & $ 0.684$ & $ 0.356$ \\
%            European & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.097$ & $ 0.526$ & $ 0.687$ & $ 0.361$ \\
%            South Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.096$ & $ 0.530$ & $ 0.691$ & $ 0.366$ \\
%        \end{longtable*}
%    \end{center}
%    \begin{itemize}
%        \item Tajima $\theta$ is the synonymous diversity.
%        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation to be under maintenance selection.
%        These mutations have a positive selection coefficient predicted at the phylogenetic-scale larger ($\Sphy > 0$), thus toward a more fit amino-acid.
%        In other words, this probability is the positive part of the DFE estimated by mutation-selection models.
%        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be positively selected.
%        These mutations have a positive selection coefficient at the population-scale larger ($\Spop > 0$), estimated from all SNPs in the population.
%        In other words, this probability is the positive part of the DFE estimated by polyDFE.
%        \item $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ is the probability for a mutation to be positively selected, given it is under maintenance selection.
%        These mutations have a positive selection coefficient at the population-scale larger ($\Spop > 0$), estimated by polyDFE on the SNPs with a positive predicted selection coefficient ($\Sphy > 0$).
%        In other words, this probability is the positive part of the DFE estimated by polyDFE, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a positive selection coefficient.
%        \item $\mathbb{P} [ \Sphy > 0 \given \Spop > 0]$ is the probability for a mutation to be under maintenance selection, given it is positively selected.
%        This probability is obtained using Bayes' formula.
%    \end{itemize}
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

>>>>

            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.116$ &              $ 1.214$ \\
            Iran &          Bos taurus &               $ 0.005$ &                $ 0.128$ &              $ 1.309$ \\
            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.130$ &              $ 1.352$ \\
            Australia &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.147$ \\
            France &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.154$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.154$ \\
            Iran &        Capra hircus &               $ 0.004$ &                $ 0.122$ &              $ 1.164$ \\
            Italy &        Capra hircus &               $ 0.003$ &                $ 0.120$ &              $ 1.148$ \\
            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.123$ &              $ 1.170$ \\
            Iran &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.210$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.112$ &              $ 1.214$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.200$ \\
            Various &          Ovis aries &               $ 0.009$ &                $ 0.112$ &              $ 1.207$ \\
            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.215$ \\
            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.122$ &              $ 1.477$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.123$ &              $ 1.501$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.494$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.491$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.503$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.123$ &              $ 1.484$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.125$ &              $ 1.528$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.123$ &              $ 1.495$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.123$ &              $ 1.493$ \\
            African &        Homo sapiens &               $ 0.003$ &                $ 0.102$ &              $ 1.676$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.669$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.682$ \\
            European &        Homo sapiens &               $ 0.002$ &                $ 0.101$ &              $ 1.659$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.676$ \\
        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).

@@

            Equus c. &      Equus caballus &               $ 0.002$ &          $ 0.017$ &                   $ 0.046$ &                                          $ 0.378$ &                         $ 0.678$ &                      $ 0.256$ \\
            Iran &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.040$ &                                          $ 0.402$ &                         $ 0.525$ &                      $ 0.211$ \\
            Uganda &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.038$ &                                          $ 0.420$ &                         $ 0.610$ &                      $ 0.256$ \\
            Australia &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.039$ &                                          $ 0.419$ &                         $ 0.368$ &                      $ 0.154$ \\
            France &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.038$ &                                          $ 0.440$ &                         $ 0.368$ &                      $ 0.162$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.040$ &                                          $ 0.418$ &                         $ 0.235$ &                      $ 0.098$ \\
            Iran &        Capra hircus &               $ 0.004$ &          $ 0.017$ &                   $ 0.033$ &                                          $ 0.500$ &                         $ 0.368$ &                      $ 0.184$ \\
            Italy &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.035$ &                                          $ 0.466$ &                         $ 0.309$ &                      $ 0.144$ \\
            Morocco &        Capra hircus &               $ 0.004$ &          $ 0.017$ &                   $ 0.032$ &                                          $ 0.514$ &                         $ 0.368$ &                      $ 0.189$ \\
            Iran &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.024$ &                                          $ 0.686$ &                         $ 0.174$ &                      $ 0.119$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &          $ 0.017$ &                   $ 0.027$ &                                          $ 0.612$ &                         $ 0.165$ &                      $ 0.101$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.031$ &                                          $ 0.542$ &                         $ 0.228$ &                      $ 0.124$ \\
            Various &          Ovis aries &               $ 0.009$ &          $ 0.017$ &                   $ 0.026$ &                                          $ 0.641$ &                         $ 0.238$ &                      $ 0.153$ \\
            Morocco &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.023$ &                                          $ 0.742$ &                         $ 0.192$ &                      $ 0.142$ \\
            Barbados & Chlorocebus sabaeus &               $ 0.004$ &          $ 0.014$ &                   $ 0.045$ &                                          $ 0.319$ &                         $ 0.595$ &                      $ 0.190$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.368$ &                         $ 0.497$ &                      $ 0.183$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.044$ &                                          $ 0.322$ &                         $ 0.502$ &                      $ 0.162$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.034$ &                                          $ 0.415$ &                         $ 0.541$ &                      $ 0.224$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.363$ &                         $ 0.492$ &                      $ 0.179$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &          $ 0.014$ &                   $ 0.041$ &                                          $ 0.345$ &                         $ 0.549$ &                      $ 0.190$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.367$ &                         $ 0.504$ &                      $ 0.185$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &          $ 0.014$ &                   $ 0.043$ &                                          $ 0.326$ &                         $ 0.538$ &                      $ 0.175$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.043$ &                                          $ 0.332$ &                         $ 0.529$ &                      $ 0.175$ \\
            African &        Homo sapiens &               $ 0.003$ &          $ 0.014$ &                   $ 0.042$ &                                          $ 0.343$ &                         $ 0.724$ &                      $ 0.249$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.040$ &                                          $ 0.358$ &                         $ 0.695$ &                      $ 0.249$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.366$ &                         $ 0.652$ &                      $ 0.239$ \\
            European &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.373$ &                         $ 0.666$ &                      $ 0.249$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.038$ &                                          $ 0.378$ &                         $ 0.677$ &                      $ 0.256$ \\

@@

    \newpage
    \begin{center}
        \captionof{table}{~}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot
            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.307$ &        $ 0.182$ &              $ 0.133$ &           $  27.0$ \\
            Iran &          Bos taurus &               $ 0.005$ &                $ 0.298$ &        $ 0.164$ &              $ 0.122$ &           $  26.1$ \\
            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.303$ &        $ 0.167$ &              $ 0.123$ &           $  26.6$ \\
            Australia &        Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.157$ &              $ 0.116$ &           $  26.4$ \\
            France &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
            Iran &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
            Italy &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
            Iran &          Ovis aries &               $ 0.007$ &                $ 0.266$ &        $ 0.179$ &              $ 0.138$ &           $  22.7$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.268$ &        $ 0.178$ &              $ 0.137$ &           $  22.8$ \\
            Various &          Ovis aries &               $ 0.009$ &                $ 0.264$ &        $ 0.180$ &              $ 0.140$ &           $  22.5$ \\
            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.303$ &        $ 0.172$ &              $ 0.126$ &           $  26.8$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  27.1$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.172$ &              $ 0.125$ &           $  27.3$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.306$ &        $ 0.172$ &              $ 0.125$ &           $  27.1$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  27.0$ \\
            African &        Homo sapiens &               $ 0.003$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.9$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.238$ &              $ 0.185$ &           $  22.0$ \\
            European &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.8$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
        \item $\mathbb{P}_{div}[\Sphy > 0]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
        \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
        \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
        This is the estimated divergence when we removed maintenance selection.
        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed maintenance selection $\dn(\Sphy < 0) / \ds$.
